Empowering Multi-Span Question Answering with Expansive Information Injection using Large Language Models

### 2024-01-16 related.tex
提交本地related_work rc修改
dev

\section{Related Work}
\label{sec:related}
In this section, we briefly summarize previous work on how Large Language Models (LLMs) such as the GPT series can be utilized as sources of knowledge and content generators to enhance and enrich text data in various application scenarios.
\subsection{Interaction with LLMs}
Large Language Models (LLMs) are powerful natural language processing models in the field of deep learning, 
characterized by their massive parameter scale and outstanding capabilities in understanding and generating natural language text. 
Recent research has highlighted the extraction of relevant knowledge from LLMs, especially in domains lacking proper coverage in knowledge bases~\citep{fang2021leveraging}. 
The application of large language models has expanded from the field of knowledge extraction to text data augmentation. 
GPT3Mix~\citep{yoo2021gpt3mix} has proposed a method that utilizes large language models to generate new text samples, thereby enhancing the performance of machine learning models.
AugGPT~\citep{dai2023auggpt} enhances natural language processing tasks in situations with limited data by interacting with ChatGPT to generate new textual data, further advancing text data augmentation.
In the realm of common sense reasoning,~\citep{liu2021generated,liu2022rainier} suggests that performance in common sense question answering can be effectively improved through prompt generation and reinforcement learning. 
Additionally, LLMs excel in generating contextual information, demonstrating the ability to create rich, 
relevant contexts based on given inputs, as validated in studies such as those by~\citep{yu2022generate}. 
The collaborative effect of iterative retrieval and generation further boosts the performance of LLMs~\citep{shao2023enhancing}. 
However, a limitation in current research is the insufficient interpretation of entities.Our study addresses this gap by interacting with ChatGPT, 
leveraging its powerful generative capabilities to design a series of prompt templates for obtaining more comprehensive entity interpretations.

In the research domain of question-answering systems, ~\citep{huang2023enhancing} improves the context learning ability of models in multi-span question-answering tasks through the introduction of answer feedback mechanisms. 
Comparisons between ChatGPT and traditional knowledge base question-answering models explore its potential as an alternative to traditional KBQA tasks~\citep{tan2023can}, 
investigating differences in providing single versus multiple answers in various contexts within reading comprehension tasks~\citep{zhang2023many}. 
Considering the limitations of LLMs in handling factual information, ~\citep{ren2023investigating} utilizes retrieval-enhanced techniques to enhance the model's understanding and response capabilities to fact-based queries.
Finally, ~\citep{wei2023zero} showcase a new approach to zero-shot information extraction through interaction with ChatGPT, 
while~\citep{liu2023once} explore the enhancement of content-based recommendation systems by combining open-source and closed-source language models. 
These studies not only demonstrate the innovation and advantages of LLMs across various domains but also provide profound insights into future research directions. 
However, the response structures generated by LLMs in these studies are not standardized. 
To address this, our prompt template design aims to ensure that the responses from ChatGPT are easily parsed and processed, enhancing the structured nature of the responses. 
Additionally, dealing with ambiguity and ambiguity is another challenge. 
Through the integration of LLM knowledge sources, our framework aims to provide clearer, more detailed information to better address semantic complexities.

>>>>

\section{Related Work}
\label{sec:related}
In this section, we briefly summarize previous work on how Large Language Models (LLMs) such as the GPT series can be utilized as sources of knowledge and content generators to enhance and enrich text data in various application scenarios.
\subsection{Interaction with LLMs}
Recent research emphasizes the significance of extracting knowledge from Large Language Models (LLMs) in domains characterized by limited knowledge base coverage~\citep{fang2021leveraging}.
GPT3Mix~\citep{yoo2021gpt3mix} extends the utility of LLMs to text data augmentation, thereby elevating the performance of machine learning models. 
AugGPT~\citep{dai2023auggpt} further contributes to natural language processing tasks in scenarios with constrained data by generating new textual data through interactions with ChatGPT.

In the realm of common-sense reasoning, the effectiveness of prompt generation and reinforcement learning has been demonstrated in enhancing question-answering performance ~\citep{liu2021generated,liu2022rainier}. 
LLMs excel in the generation of contextual information ~\citep{yu2022generate}, 
and the collaborative impact of iterative retrieval and generation amplifies overall LLM performance~\citep{shao2023enhancing}.

Within question-answering systems, ~\citep{huang2023enhancing} improve model context learning in multi-span tasks through answer feedback mechanisms. 
Comparative analyses between ChatGPT and traditional knowledge base question-answering models explore its potential as an alternative~\citep{tan2023can}. 
In addressing LLM limitations in handling factual information, ~\citep{ren2023investigating} employ retrieval-enhanced techniques to enhance the model's understanding of fact-based queries.

~\citep{wei2023zero} showcase zero-shot information extraction through ChatGPT interaction, 
while~\citep{wei2023zero} explore enhancing content-based recommendation systems by combining open-source and closed-source language models. 
Collectively, these studies highlight LLM innovation across diverse domains, offering valuable insights for future research.

However, challenges persist, including non-standardized response structures and ambiguity. 
Our research focuses on designing a set of templates for interacting with ChatGPT, encompassing entity interpretation, entity relationship analysis, rewriting, and summary information for each task. 
Additionally, we introduce a knowledge injection method to directly incorporate knowledge generated by large models into training texts, thereby enhancing task performance. 
This approach aims to provide a structured and comprehensive framework for leveraging LLMs in various applications.
